Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2018-03-12 manuscript.Rnw
Fix figure captions for func div

\noindent\fig \ref{fig:CWM}. Mean values of selected functional morphological traits of epiphytic and
terrestrial ferns on Moorea, French Polynesia. Epiphytic values in green, terrestrial
values in brown. A) Community-weighted mean (CWM) values for each trait plotted
against either minimum relative humidity ($\n = 13$ communities each for epiphytes and
terrestrial species) or elevation ($\n = 17$ communities each). Trendlines indicate
significant relationships determined by a linear model at $\pval<0.05$. B) Mean values for all
species by growth habit for each trait. Numbers of species with observations available
differed for each trait and are shown at bottom of each barplot. Asterisks indicate
statistical significance of one-sided \tval-test; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.
Trends for three leaf size traits (stipe length, frond length, and frond with) were
quantitatively very similar, so of these we only present stipe length.
\vspace{\baselineskip}

\noindent\fig \ref{fig:FDIV}. Functional and phylogenetic diversity of epiphytic and terrestrial fern
communities on Moorea, French Polynesia. Epiphytic communities in green, terrestrial
communities in brown. Response variable abbreviations as follows: MPD, standard effect
size (SES) of mean phylogenetic distance; MNTD, SES of mean nearest taxon distance;
FRic, functional richness; FEve, functional evenness; FDiv, functional diversity. A)
Response variables plotted against either minimum relative humidity ($\n = 13$
communities each for epiphytes and terrestrial species) or elevation ($\n = 17$ communities
each). Trendlines indicate significant relationships determined by a linear model at $\pval<0.05$. B) Median values (box plots) of response variables by growth habit (epiphytic or
terrestrial) across all communities (epiphytic communities, $\n = 17$; terrestrial
communities, $\n = 17$). Medians shown with bold lines, lower and upper hinges
correspond to first and third quartiles, and whiskers extend to values within 1.5 $\times$ the
interquartile range. Asterisks indicate statistical significance of one-sided \tval-test; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.

>>>>

\noindent\fig \ref{fig:CWM}. Change in selected functional traits of ferns on Moorea, French Polynesia across environmental gradients and between growth habit types (epiphytic or terrestrial). Epiphytic values in green, terrestrial
values in brown. Scatterplots show community-weighted mean (CWM) values for each trait plotted
against either minimum relative humidity ($\n = 13$ communities each for epiphytes and
terrestrial species) or elevation ($\n = 17$ communities each). Trendlines indicate
significant relationships determined by a linear model at $\pval<0.05$. Barplots show mean values for all
species by growth habit (epiphytic or
terrestrial) for each trait. Error bars show standard error. Asterisks indicate
statistical significance of two-sided \tval-test for differences between epiphytic and terrestrial species; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.
Trends for three leaf size traits (stipe length, frond length, and frond with) were
quantitatively very similar, so of these we only present stipe length.
\vspace{\baselineskip}

\noindent\fig \ref{fig:FDIV}. Functional and phylogenetic diversity of epiphytic and terrestrial fern
communities on Moorea, French Polynesia. Epiphytic communities in green, terrestrial
communities in brown. Response variable abbreviations as follows: MPD, standard effect
size (SES) of mean phylogenetic distance; MNTD, SES of mean nearest taxon distance;
FRic, functional richness; FEve, functional evenness; FDiv, functional diversity. Scatterplots show
response variables plotted against either minimum relative humidity ($\n = 13$
communities each for epiphytes and terrestrial species) or elevation ($\n = 17$ communities
each). Trendlines indicate significant relationships determined by a linear model at $\pval<0.05$. Boxplots show median values (bold lines) of response variables by growth habit (epiphytic or
terrestrial) across all communities (epiphytic communities, $\n = 17$; terrestrial
communities, $\n = 17$). Lower and upper hinges
correspond to first and third quartiles, and whiskers extend to values within 1.5 $\times$ the
interquartile range. Asterisks indicate statistical significance of one-sided \tval-test; $*** = \pval<0.001$; $** = \pval<0.01$; $* = \pval<0.05$.
